---
title: "Command line"
session: "09"
subtitle: "Adapted from slides by Alison Hill (RStudio)"
author: Zoë Turner
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default", "assets/css/my-theme.css", "assets/css/my-fonts.css"]
    seal: false 
    lib_dir: libs
    nature:
      highlightStyle: dracula
      highlightLanguage: ["r", "yaml", "markdown"]
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
    includes:
      in_header: assets/header.html  
params:
  site_link: "https://philosopher-analyst.netlify.app/rmd-workshop/"
  cloud_link: "https://rstudio.cloud/"
  github_link: "https://github.com/Lextuga007/rm_01_basics"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
episode_counter <- 0
knitr::opts_chunk$set(
  collapse = TRUE,   
  comment = "#>"
)
```

```{r packages, include=FALSE}
library(countdown)
library(ymlthis)
library(tidyverse)
library(bakeoff)
library(xaringanExtra)

xaringanExtra::use_clipboard()
xaringanExtra::use_share_again() # need to get the slide button on html view
```

class: title-slide, center, middle

<span class="fa-stack fa-4x">
  <i class="fa fa-circle fa-stack-2x" style="color: #ffffffcc;"></i>
  <strong class="fa-stack-1x" style="color:#e7553c;">`r rmarkdown::metadata$session`</strong>
</span> 

# `r rmarkdown::metadata$title`

---
class: inverse, center, middle

# <center>Command line</center>

<span class="fa-stack fa-4x">
  <i class="fa fa-circle fa-stack-2x" style="color: #fff;"></i>
  <strong class="fa-stack-1x" style="color:#17a2b8;">`r (episode_counter <- episode_counter + 1)` </strong>
</span> 

---
class: middle, center

# Rendering

.pull-left[

So far we've used the RStudio button to `r emo::ji("yarn")`  

What about on the command line?
]



--

.pull-right[
```{r eval=FALSE}
rmarkdown::render("01-bakeoff-report.Rmd")
```

]

---
class: your-turn

# Your turn

Instead of using the "Knit" button, try running this code in your R console:

```{r eval = FALSE}
library(rmarkdown) # needs to be loaded first
render("01-bakeoff-report.Rmd")

# or

rmarkdown::render("01-bakeoff-report.Rmd")
```

Now try changing the parameters:

```{r eval = FALSE}
render("01-bakeoff-report.Rmd",
       params = list(series = "9"))
```

__If this was easy__, play with the other parameters too. Or see if you can change the output format, and add output option `toc = TRUE`.

_psst...answers on the next slide..._


```{r echo = FALSE}
countdown(minutes = 5)
```

???
The rendered document doesn't appear in a pop up and you will have to click on the newly created `01-bakeoff-report.html` which corresponds to the `.rmd` file. 

A hint for finding the parameters to a function is to select F1 when the cursor is in the word `render`. 

The help files will appear in the bottom right panel of RStudio.

---
class: your-turn

# Example answer

```{r eval=FALSE}
render("01-bakeoff-report.Rmd",
       params = list(series = "9"), 
       output_format = "word_document")
```

---
class: middle, center

# Take-aways

--

`r emo::ji("heavy_check_mark")` **Documents run sequentially** the order of your code chunks matters

--

`r emo::ji("heavy_check_mark")` **Click or code** the flexibility of RMarkdown is that you can use RStudio or code in the console

--

`r emo::ji("exclamation")` **RMarkdowns are self-contained** any data use needs to be coded in the script and not "pre-loaded" in RStudio

--

`r emo::ji("exclamation")` **Manual parameters overwrite the output** each output needs to be saved individually - this can be laborious

---

class: middle, center

# `r emo::ji("stopwatch")`

# Time for a break!

```{r echo = FALSE}
countdown(minutes = 10)
```

---

class: inverse

# <center>Next section...</center>
